Presentation Title

### 2017-08-20 thesis/chapters/ch5-implementation.tex
Edit everything

We evaluate our system experimentally to ultimately understand its scalability characteristics as well as limitations.
Concretely,
we give an open source prototype implementation that runs on a network with over 1000 node.
Nodes in our implementation make transactions autonomously with each other and then we collect the results for analysis.

This chapter begins with a description of the implementation in \Cref{sec:implementation}.
Then, we describe our experimental setup in \Cref{sec:experimental-setup},
which includes a discussion on the system parameters and the physical infrastructure which we use.
Finally, \Cref{sec:comms-cost-experiment} and onwards follows the same structure as \Cref{sec:performance-analysis},
where we analyse the performance experimentally rather than analytically and compare the results.

@@

The goal of the experiment is to run the three protocols---consensus protocol,
transaction protocol and validation protocol---simultaneously and analyse the communication cost, the consensus duration and the global throughput.
We investigate these properties under the following parameters.
\begin{enumerate}
  \item The number of facilitators $n \in \{4, 8, \dots, 32\}$.
        The maximum $n$ is 32 because the limitation in liberasurecode mentioned in \Cref{sec:implementation},
        but our results give a good indication of how our system may function for larger numbers of $n$.
  \item The population size $N \in \{200, 300, \dots, 1200\}$.
        $N$ stops at 1200 is due to our physical setup, which we describe next.
  \item The two modes of transaction.
        The first mode is the \emph{fixed-neighbour} mode where nodes only transact with their immediate neighbour which is predetermined. 
        This minimises the data volume per validated transaction because agreed fragment can be cached.
        The second mode is in the other extreme which we call the \emph{random-neighbour} mode,
        where every transaction is with a random node out of the $N$ nodes in the system.
        It is unlikely that the agreed fragments can be reused.
\end{enumerate}

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-comms-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-comms-random}
    \end{subfigure}%
  }
  \caption{Communication cost for the consensus protocol per round increases linearly with population size.
  The error bars are larger for higher population size or higher number of facilitators is because rounds take longer thus they are repeated fewer times.}
  \label{fig:round-comms}
\end{figure}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-duration-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-duration-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-duration-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-duration-random}
    \end{subfigure}%
  }
  \caption{Round duration does not increase linearly with the population size,
  which is likely due to the additional hashing operation required for larger consensus result.}
  \label{fig:round-duration}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/tx-communication-cost-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:tx-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/tx-communication-cost-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:tx-comms-random}
  \end{subfigure}
  }
  \caption{Communication cost per verified transaction has similar (near linear) trend as~\Cref{fig:round-duration}.
  Fluctuation for the fixed-neighbour mode exists because the cache mechanism is unpredictable.}
  \label{fig:tx-comms}
\end{figure}

@@

More interestingly, there is a large difference in communication cost between the two modes of transaction.
When transacting with only one neighbour, the communication cost is low because only one agreed fragment needs to be communicated for every round in order to validate all transactions of that round,
which is because agreed fragments are cached.
On the other hand,
if every node is transacting with a random node, then it is likely the case that one agreed fragment needs to be communicated for every transaction.
Hence the communication cost we see in~\Cref{fig:tx-comms-random} is much higher than in~\Cref{fig:tx-comms-fixed}.

Some fluctuations exist in~\Cref{fig:tx-comms-fixed}, this is due to our caching mechanism.
We send validation requests at the same rate as transactions.
Upon receiving a (remote) agreed fragment, the caching mechanism inspects all the transactions in the agreed fragment and attempts to verify as many as it can,
rather than just the transaction in the original validation request.
However, it may be the case that the agreed fragments arrive later than the validation request interval.
Then it is possible to have sent two or more validation requests for some transactions in the same local agreed fragment.
In this case, the remote would respond with two or more of the same agreed fragments,
which results in extra (wasted) communication cost, and this is the source of the fluctuation seen in~\Cref{fig:tx-comms-fixed}.
The result in~\Cref{fig:tx-comms-random} reinforces our argument.
It is a lot more stable because for every transaction it is almost always the case that an agreed fragment is needed to validate it.

\section{Linear global throughput}
\begin{figure}[h]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Using fixed neighbours results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure}

@@

Note that the throughput decreases slightly as the number of facilitators increases,
which is due to the additional communication cost for running ACS with a high number of facilitators.
That is, if the network is congested then the nodes may not have enough bandwidth to send validation responses timely.

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{Transactions are with random neighbours.}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{A limitation of our system is when nodes are transacting with many random nodes,
  then the network cannot keep up with the large number of agreed fragments that need to be communicated between nodes.
  Hence the slope of validated transactions grows at a slower rate in~\Cref{fig:backlog-random}.}
  \label{fig:backlog}
\end{figure}

\section{Communication cost with varying number of facilitators}
Up to this point we focused on the effect of communication cost, throughput and so on with respect to the population size.
In this section, we consider a varying number of facilitators,
which gives us an insight into our system performance may perform when the number of facilitators is higher than 32.

@@

\Cref{fig:facilitators-round-comms} shows the communication cost of the consensus protocol for varying numbers of facilitators.
There is strong evidence that the communication cost grows polynomially.
We expect this because of there are polynomial terms in the ACS communication complexity---$O(n^2|v| + \lambda n^3 \log n)$.
This also means that the rounds would take longer to complete and transactions would take longer to verify.
On the other hand, we get better fault tolerance.
Thus a linear increase in fault tolerance ($t$) costs a polynomial increase in communication cost.

>>>>

We evaluate our system experimentally to ultimately understand its scalability characteristics as well as its limitations.
Concretely,
we give an open source prototype implementation that runs on a network with over 1000 node.
Nodes in our implementation make transactions autonomously with each other and then we collect the results for analysis.

This chapter begins with a description of the implementation in \Cref{sec:implementation}.
Then, we describe our experimental setup in \Cref{sec:experimental-setup},
which includes a discussion on the system parameters and the physical infrastructure which we use.
Finally, \Cref{sec:comms-cost-experiment} and onwards follows the same structure as \Cref{sec:performance-analysis},
where we analyse the performance experimentally.

@@

The goal of the experiment is to run \textsc{Checo} and analyse the communication cost, the consensus duration and the global throughput.
We investigate these properties under the following parameters.
\begin{enumerate}
  \item The number of facilitators $n \in \{4, 8, \dots, 32\}$.
        The maximum $n$ is 32 because the limitation in liberasurecode mentioned in \Cref{sec:implementation},
        but our results in~\Cref{sec:varying-facilitator-experiment} give a good indication of how our system may function for a larger $n$.
  \item The population size $N \in \{200, 300, \dots, 1200\}$.
        $N$ stops at 1200 is due to our physical setup, which we describe next.
  \item The two modes of transaction.
        The first mode is the \emph{fixed-neighbour} mode where nodes only transact with one predetermined node. 
        This minimises the data volume per validated transaction because agreed fragment can be cached.
        The second mode is in the other extreme which we call the \emph{random-neighbour} mode,
        where every transaction is with a random node out of the $N$ nodes in the system.
        It is unlikely that the agreed fragments can be reused.
\end{enumerate}

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-communication-cost-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-comms-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-communication-cost-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-comms-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the communication cost per round for the consensus protocol.
  The error bars are larger for higher population size or higher number of facilitators is because rounds take longer thus they are repeated fewer times.}
  \label{fig:round-comms}
\end{figure}

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
    \begin{subfigure}[b]{.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-fixed/round-duration-vs-population}
      \caption{Transactions are with fixed neighbours.}
      \label{fig:round-duration-fixed}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{neighbour-random/round-duration-vs-population}
      \caption{Transactions are with random neighbours.}
      \label{fig:round-duration-random}
    \end{subfigure}%
  }
  \caption{Experimental result of the round duration per round for the consensus protocol.}
  \label{fig:round-duration}
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/tx-communication-cost-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:tx-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/tx-communication-cost-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:tx-comms-random}
  \end{subfigure}
  }
  \caption{Experimental result of the communication cost per verified transaction.
  It has a similar, near linear, trend as~\Cref{fig:round-duration}.
  Fluctuation for the fixed-neighbour mode exists because the cache mechanism is unpredictable.}
  \label{fig:tx-comms}
\end{figure}

@@

More interestingly, there is a large difference in communication cost between the two modes of transaction.
When transacting with only one neighbour, the communication cost is low because only one agreed fragment needs to be communicated for every round in order to validate all transactions of that round.
On the other hand,
if every node is transacting with a random node, then it is likely the case that one agreed fragment needs to be communicated for every transaction.
Hence the communication cost we see in~\Cref{fig:tx-comms-random} is much higher than in~\Cref{fig:tx-comms-fixed}.

Some fluctuations exist in~\Cref{fig:tx-comms-fixed}, this is due to our caching mechanism.
We send validation requests at the same rate as transactions.
Upon receiving a (remote) agreed fragment, the caching mechanism inspects all the transactions in the agreed fragment and attempts to verify as many as it can,
rather than just the transaction in the original validation request.
However, it may be the case that the agreed fragments arrive later than the validation request interval.
Then it is possible to have sent two or more validation requests for some transactions in the same local agreed fragment.
In this case, the remote would respond with two or more of the same agreed fragments,
which results in extra (wasted) communication cost, and this is the source of the fluctuation seen in~\Cref{fig:tx-comms-fixed}.
The result in~\Cref{fig:tx-comms-random} reinforces our argument.
It is a lot more stable because for every transaction it is almost always the case that a new agreed fragment is needed to validate it.

\section{Linear global throughput}
\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput increases as the population increases when every node transact at the same rate.
  Using fixed neighbours results in a higher throughput because of the caching mechanism.}
  \label{fig:global-throughput}
\end{figure}

@@

Note that the throughput decreases slightly as the number of facilitators increases.
This effect is due to the additional communication cost for running ACS with a high number of facilitators.
That is, if the network is congested then the nodes may not have enough bandwidth to send validation responses timely.

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{Transactions are with random neighbours.}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{Demonstration of the network bottleneck.
  Note that the slope of validated transactions grows at a slower rate in~\Cref{fig:backlog-random} than in~\Cref{fig:backlog-fixed}.}
  \label{fig:backlog}
\end{figure}

\section{Communication cost with varying number of facilitators}
\label{sec:varying-facilitator-experiment}
Up to this point we focused on the effect of communication cost, throughput and so on with respect to the population size.
In this section, we consider a varying number of facilitators,
which gives us an insight into our system performance may perform when the number of facilitators is higher than 32.

@@

\Cref{fig:facilitators-round-comms} shows the communication cost of the consensus protocol for varying numbers of facilitators.
There is strong evidence that the communication cost grows polynomially.
We expect this behaviour because of there are polynomial terms in the ACS communication complexity---$O(n^2|v| + \lambda n^3 \log n)$.
This also means that the rounds would take longer to complete and transactions would take longer to verify.
On the other hand, we get better fault tolerance.
Thus a linear increase in fault tolerance ($t$) costs a polynomial increase in communication cost.

### 2017-08-20 thesis/chapters/ch6-conclusion.tex
Edit everything

In this work we introduced an application neutral blockchain system which we call \textsc{Checo}.
We add checkpoint block to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

This work answers the research question stated in~\Cref{ch:problem}.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}
Concretely, fault tolerance is guaranteed if $n \ge 3t + 1$ by using ACS as a building block.
While $t$ may be small compared to the population size $N$,
we show that the probability for the system to fail is low even when $n \ge 3t + 1$ does not hold as long as the proportion of malicious nodes is not close to a third of $N$.
For example, if there the population size is 1000 and 20\% of the nodes are malicious,
the probability for a round to potentially to fail is bounded below $2.6 \times 10^{-16}$.
This probability bound would decrease as the population size increases.
Horizontal scalability property is demonstrated both analytically and experimentally.
Unlike sharding protocols, the property holds regardless of transaction characteristics and needs no parameter selection.
Finally, we achieve global consensus on transactions via consensus on checkpoint blocks.

@@

Our experiment is carried out in a somewhat idealised world (DAS-5).
We hope to experiment our prototype in a more realistic environment.
For example, DeterLab~\cite{mirkovic2012teaching} lets users simulate network delay,
which is important for discovering issue that may only occur in hostile environments.
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the TrustChain in Tribler stores the number of bytes uploaded and downloaded between users, but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

The fault tolerance property is adequate for permissioned systems where nodes have relatively more trust between each other.
However, it is not adequate for permissionless systems,
which usually aim to tolerate fault that involve a minority of the network,
which can be just shy of 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme which means that nodes with more stake in the system get more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.

>>>>

In this work we introduced an application neutral blockchain system which we call \textsc{Checo}.
We add checkpoint block to the existing TrustChain data structure to capture the system state.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

This work answers the research question stated in~\Cref{sec:research-question}.
\begin{displayquote}
\emph{How can we design a blockchain consensus protocol that is fault-tolerant,
horizontally scalable,
and able to reach global consensus?}
\end{displayquote}
Concretely, fault tolerance is guaranteed if $n \ge 3t + 1$ by using ACS as a building block.
While $t$ may be small compared to the population size $N$,
we show that the probability for the system to fail is low even when $n \ge 3t + 1$ does not hold as long as the proportion of malicious nodes is not close to a third of $N$.
The horizontal scalability property is demonstrated both analytically and experimentally.
Unlike sharding protocols, the property holds regardless of transaction characteristics and needs no parameter selection.
Finally, we achieve global consensus on transactions via consensus on checkpoint blocks.

@@

Our experiment is carried out in a somewhat idealised world (DAS-5).
We hope to experiment our prototype in a more realistic environment.
For example, DeterLab~\cite{mirkovic2012teaching} lets users simulate network delay,
which is important for discovering issue that may only occur in hostile environments.
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the standard TrustChain in Tribler is used for accounting internet traffic between users,
but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

The fault tolerance property is adequate for permissioned systems where nodes have relatively more trust between each other.
However, it is not adequate for permissionless systems,
which usually aim to tolerate fault that involve a minority of the network,
which can be just shy of 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme (e.g., Ouroboros~\cite{kiayias2017ouroboros}) which means that nodes with more stake in the system get more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.

### 2017-08-20 thesis/formalities/abstract.tex
Edit everything

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains individual hash chains,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the individual hash chains,
thus a single checkpoint block may represent a large set of transaction blocks.
The consensus protocol does not imply transaction validity.
Hence we include a validation protocol which allows nodes to verify that transactions are correctly recorded,
which indirectly achieves consensus on transactions.
% how good is the solution?
We implement a prototype and evaluate it experimentally.
Our results show a strong indication of horizontal scalability even in the worst case,
where every transaction is made with a randomly selected node.
\end{abstract}

>>>>

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains a personal hash chain,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the personal hash chains,
thus a single checkpoint block may represent a large set of transactions.
The consensus protocol does not imply transaction validity.
Hence we introduce a validation protocol which allows nodes to verify that the transactions are correctly recorded,
meaning that consensus on transactions is achieved indirectly via checkpoint blocks.
% how good is the solution?
We evaluate \textsc{Checo} analytically and experimentally.
Our results show a strong indication of horizontal scalability even in the worst case,
where every transaction is made with a randomly selected node.
\end{abstract}

### 2017-08-20 thesis/formalities/preface.tex
Edit everything

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, when I mined my first Bitcoin, 
I have been interested in decentralising the traditionally centralised systems.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

@@

\noindent
There are a number of people who have supported me in this endeavour who I would like to thank.
My supervisor Dr. Johan Pouwelse, your unrivalled enthusiasm and guidance have kept me motivated and productive.
Dr. Zhijie Ren, this work would not have been possible without your invaluable input and the numerous discussions which we have had.
Members of the Tribler team---Martijn de Vos, Quinten Stokkink and Chengxin Ma,
you have my gratitude for helping me with the implementation and proofreading my work.
Members of the Cyber Security group---Dr. Zekeriya Erkin and O\u{g}uzhan Ersoy,
I thank both of you for your feedback on my presentations.

>>>>

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, the time when I mined my first Bitcoin, 
I became cautious of the security and privacy issues surrounding centralised systems,
and became interested in building a decentralised society.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

@@

\noindent
There are a number of people who have supported me in this endeavour who I would like to thank.
My supervisor Dr. Johan Pouwelse, your unrivalled enthusiasm and guidance have kept me motivated and productive.
Dr. Zhijie Ren, this work would not have been possible without your invaluable input and the numerous discussions which we have had.
Prof. Dick Epema, you taught me a lot on report writing and the use (and misuse) of mathematical formalism.
Members of the Tribler team---Martijn de Vos, Quinten Stokkink and Chengxin Ma,
you have my gratitude for helping me with the implementation and proofreading my work,
and of course the free coffee.
Members of the Cyber Security group---Dr. Zekeriya Erkin and O\u{g}uzhan Ersoy,
I thank both of you for your feedback on my presentations.
